Blas\'e3D

### 2023-11-07 paper/paper2/ms.tex
Paper symbol table

\usepackage{amsmath}
\usepackage{blindtext}
% Temporary packages
\usepackage{mdframed}

@@

\appendix
\section{Linear Regression}
\blindtext

>>>>

\usepackage{amsmath}
\usepackage{blindtext}
\usepackage{bm}
% Temporary packages
\usepackage{mdframed}
\usepackage{verbatim}

\def\Teff{T_{\rm eff}}
\def\vsini{v\sin{i}}
\def\kmps{\mathrm{km}\;\mathrm{s}^{-1}}

@@

\appendix
\section{Notation}
We adopt similar notation to the blas\'e paper, with some small modifications.

\begin{deluxetable}{cp{10cm}}[h]
    \tabletypesize{\small}
    \tablecaption{Notation used in this paper\label{table2}}
    \tablehead{
        \colhead{Symbol} & \colhead{Meaning}
    }
    \startdata
    \hline
    \multicolumn{2}{c}{Indexes}\\
    \hline
    $i$ & Pixel index of the precomputed spectrum\\
    $j$ & Spectral line index\\
    $k$ & Grid point index\\
    \hline
    \multicolumn{2}{c}{Spectra}\\
    \hline
    $\bm{\lambda}$ & Spectral axis of the model grid\\
    $\mathbb{G}$ & The grid of synthetic spectral models\\
    $\mathsf{B}_k$ & Blackbody spectrum of the $k^{th}$ model\\
    $\mathsf{P}_k$ & Continuum polynomial of the $k^{th}$ model\\
    $\mathsf{S}_k$ & Preprocessed flux vector of the $k^{th}$ model\\
    $\mathsf{\hat{S}}$ & Flux vector of the continuous model reconstruction\\
    $\mathsf{R}_k$ & Residual between a $\mathsf{S}_k$ and its reconstruction\\
    \hline
    \multicolumn{2}{c}{Spectral Line Properties}\\
    \hline
    $\mu_{jk}$ & Center position of the $j^{th}$ line in the $k^{th}$ model\\
    $A_{jk}$ & Amplitude of the $j^{th}$ line in the $k^{th}$ model\\
    $\sigma_{jk}$ & Gaussian shape parameter of the $j^{th}$ line in the $k^{th}$ model\\
    $\gamma_{jk}$ & Lorentzian shape parameter of the $j^{th}$ line in the $k^{th}$ model\\
    \hline
    \multicolumn{2}{c}{Scalars}\\
    \hline
    $I$ & Number of pixels in the model grid's spectral axis\\
    $J$ & Number of spectral lines detected across the grid \\
    $K$ & Number of grid points in the model grid\\
    $p$ & The prominence threshold of spectral lines to identify\\
    $v\sin(i)$ & Observed stellar rotation for inclination $i$ and true rotation $v$\\
    $v_r$ & Radial velocity of the star\\
    $R$ & Spectrograph resolving power $\lambda/\delta\lambda$\\
    $Q$ & Quality of a spectral reconstruction\\
    $H$ & The average storage impact of a spectral reconstruction\\
    $T$ & The average computational impact of a spectral reconstruction\\
    \enddata
\end{deluxetable}
